---
title: "drug_AOP"
author: "Bagdad Youcef,WU Qier"
date: "19/02/2021"
output:
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(reticulate)
library(igraph)
```


--------------------------------------It need to change some variables depending on your table----------------------------------
# Data input
```{r}
nbr_event_classs=3 #number of AOP event class

drug_tar_table=read.delim('infertility.txt',sep='\t',dec=".",header = T)
drug_tar_table
unique(length(table(drug_tar_table$Event.type)))
sum(is.na(drug_tar_table))
diff_fmls=table(drug_tar_table$Event.type)
tab_1=drug_tar_table[which(drug_tar_table$Event.type==names(diff_fmls[1])),]
for (i in (2:length(table(diff_fmls)))){
  tab_=drug_tar_table[which(drug_tar_table$Event.type==names(diff_fmls[i])),]
  tar_nm_tab=rbind(tab_1,tab_)
  tab_1=tar_nm_tab
}
diff_fmls


```

```{r}
nbr_lignes2=sum(diff_fmls[1:nbr_event_classs])
tab_donnees2=tar_nm_tab[1:nbr_lignes2,]
tab_donnees2

```
```
infertility table:
Drug.Name	Event.ID	Event.name	Event.type
Finasteride	1688	decrease, male anogenital distance	AdverseOutcome
Flutamide	1688	decrease, male anogenital distance	AdverseOutcome
Dexamethasone	1688	decrease, male anogenital distance	AdverseOutcome
Ketoconazole	1688	decrease, male anogenital distance	AdverseOutcome
Antagonism, Androgen receptor	1614	Decrease, AR activation	NewKeyEvent
Decrease, AR activation	1687	decrease, transcription of genes by AR	NewKeyEvent
decrease, transcription of genes by AR	1688	decrease, male anogenital distance	AdverseOutcome
Decrease, AR activation	26	Antagonism, Androgen receptor	MolecularInitiatingEvent
decrease, transcription of genes by AR	1614	Decrease, AR activation	NewKeyEvent
decrease, male anogenital distance	1687	decrease, transcription of genes by AR	NewKeyEvent
5alpha-reductase, inhibition	1613	Decrease, DHT level	NewKeyEvent
Decrease, DHT level	1614	Decrease, AR activation	NewKeyEvent
Decrease, AR activation	286	Altered, Transcription of genes by AR	NewKeyEvent
Altered, Transcription of genes by AR	1688	decrease, male anogenital distance	AdverseOutcome
Decrease, DHT level	1617	5alpha-reductase, inhibition	MolecularInitiatingEvent
Decrease, AR activation	1613	Decrease, DHT level	NewKeyEvent
Altered, Transcription of genes by AR	1614	Decrease, AR activation	NewKeyEvent
decrease, male anogenital distance	286	Altered, Transcription of genes by AR	NewKeyEvent
```

```{r}
tar_nm=tab_donnees2$Event.name
drg_nm=tab_donnees2$Drug.Name
dr_class=tab_donnees2$Event.type
dr_id=tab_donnees2$Event.ID
```


## this part is to change variables in R to python
```{python}
tar_nm_py=r.tar_nm 
drg_nm_py=r.drg_nm
dr_class_py=r.dr_class
```

## bipartite network

```{python}
dic_tar_class={}
co=0
for tar in (tar_nm_py):   
  if(tar not in dic_tar_class.keys()):
    dic_tar_class[tar]=dr_class_py[co]
  co=co+1

```

```{python}
sm1=[]
sm2=[]
sm3=[]
sm4=[]
list_pass=[]
for a in range(len(tar_nm_py)):
  ar=[tar_nm_py[a],drg_nm_py[a]]
  if(ar not in list_pass and ([drg_nm_py[a],tar_nm_py[a]] not in list_pass ) and drg_nm_py[a]!= tar_nm_py[a]):
    list_pass.append(ar)
    sm1.append(tar_nm_py[a])
    sm2.append(drg_nm_py[a])
    sm3.append("interact")
    sm4.append(dic_tar_class[tar_nm_py[a]])
    
```


```{r}
df_gr_bipartite=data.frame(drug=py$sm2,AOP_event=py$sm1,interaction=py$sm3,AOP_event_type=py$sm4)

#write.table(df_gr_bipartite,file="graph_bipartite.txt",quote = F,row.names = F,sep = "\t")

```

--------------------------------------------------increase in uncertainty ---------------------------------------------
#H before calculation

## Hbefore for graph :

-vertex1: drug name
-vertex2: AOP event

```{python}

def tous_linkages_paterns(vertex1,vertex2):
  linkage_paterns={}
  for r in range(len(vertex1)):
    linkage_paterns[vertex1[r]]=[]
  lp_drugs_list=[]
  for pos in range(len(vertex1)):
        if(vertex2[pos] not in linkage_paterns[vertex1[pos]]):
          linkage_paterns[vertex1[pos]].append(vertex2[pos])
          
  return linkage_paterns

```

### linkage patterns in bipartite graph

```{python}
def redon_lp(values_list_lp2): 
  red_lp2={} 
  liste_pass=[]
  co=0
  for lp in values_list_lp2:
    if(lp not in liste_pass): 
      liste_pass.append(lp)
      red_lp2[co]=values_list_lp2.count(lp)
      co=co+1
  return (red_lp2,liste_pass)

```


```{python}
import math

def calcul_h_before(drg_nm_py,tar_nm_py):
  linkage_paterns2=tous_linkages_paterns(drg_nm_py,tar_nm_py) #list of linkage patterns

  values_list_lp2=[] #all the linkage patterns
  for key in linkage_paterns2:
    val_lp_sort=sorted(linkage_paterns2[key])
    values_list_lp2.append(val_lp_sort)


  red=redon_lp(values_list_lp2) 
  red_lp2=red[0]
  list_ts_lp=red[1]
  H_before2=0
  for keyss in red_lp2:
    H_before2=H_before2+(red_lp2[keyss]/sum(red_lp2.values()))*(math.log(red_lp2[keyss]/sum(red_lp2.values())))
  H_before2=-H_before2
  return (H_before2, values_list_lp2,list_ts_lp)
```


### result: Hbefore for global graph 
```{python}
  
clc_h=calcul_h_before(drg_nm_py,tar_nm_py)

values_list_lp2=clc_h[1]
H_before2=clc_h[0]
# Hbefore for global graph 
H_before2
```
```
H_before2: 1.7677614722893296
```

```{python}
len(values_list_lp2) #number of linkage patterns in the graph 
```
```
len(values_list_lp2)=11
```


# calculate Hbefore for each vertex

number of vertices in graph
-length(ts_tar): all your number AOP event; length(ts_drug): all your number of drugs
-attention: if you calculate loss information with KER, here length(ts_drug)=number of vertices in graph
```{r}
ts_tar=names(table(tar_nm))
ts_drug=names(table(drg_nm))
nbr_vertexs=length(ts_tar)+length(ts_drug)
#or nbr_vertexs=length(ts_drug)
length(ts_tar)
length(ts_drug)
```
```
length(ts_tar)=7 (number of AOPevent)
length(ts_drug)=11 (number of drug+AOPevent)
```

```{python}
import pandas as pd
Hbefore_vertices=pd.DataFrame(columns=['h_bfr','event'])
```


```{python}
import math
co=0
list_h_bfr_ch_tar=[]
list_vrai_tar=[]
ts_tar=r.ts_tar
for tar in ts_tar:
  for lp in values_list_lp2:
    if(tar in lp ):
      co=co+1
  if(co!=0):
    h_tar=(co/len(values_list_lp2))*math.log(co/len(values_list_lp2))
    list_h_bfr_ch_tar.append(-h_tar)
    list_vrai_tar.append(tar)
    Hbefore_vertices=Hbefore_vertices.append({'event': tar,'h_bfr': -h_tar}, ignore_index=True)
  co=0
print(list_h_bfr_ch_tar)
```
```
[Antagonism, Androgen receptor: 0.217990479345306, Altered, Transcription of genes by AR: 0.309954198588805, Decrease, DHT level: 0.309954198588805, decrease, transcription of genes by AR: 0.309954198588805, 5alpha-reductase, inhibition: 0.217990479345306, decrease, male anogenital distance: 0.330619529220172, Decrease, AR activation: 0.367854876973993]
```

```{r}
Hbefore_vertices<-py$Hbefore_vertices
Hbefore_vertices<-unique(Hbefore_vertices)
#write.table(Hbefore_vertices,"h_before_vertices.txt",row.names = F,sep="\t",quote=F)
```

```{python}

dic_tar_class={}
co=0
for tar in (tar_nm_py):  
  if(tar not in dic_tar_class.keys()):
    dic_tar_class[tar]=dr_class_py[co]
  co=co+1

```



```{r}
event_type=names(table(dr_class))[1:nbr_event_classs]
event_type

```
```
["AdverseOutcome", "MolecularInitiatingEvent" "NewKeyEvent" ]
```

```{python}
dic_h_bfr={}
for i in r.event_type:
  dic_h_bfr[i]=0
```


```{python}

i=0
for event_class in r.event_type:
  for tar in list_vrai_tar:
    if(dic_tar_class[tar]==event_class):
      dic_h_bfr[dic_tar_class[tar]]=dic_h_bfr[dic_tar_class[tar]]+list_h_bfr_ch_tar[i]
    i=i+1
  i=0


```

# monopartite graph projection

```{python}
une_erete=[]
list_art=[]
list_art_avc_red=[] 
for list_liaison in values_list_lp2:
  if(len(list_liaison)!=1): 
    for adv in list_liaison:
      for adv2 in list_liaison:
        if(adv!=adv2):
          une_edge=[adv,adv2]
          if([adv2,adv] not in list_art_avc_red):
            list_art_avc_red.append(une_edge)
          if(une_edge not in list_art and [adv2,adv] not in list_art): 
            list_art.append(une_edge)

#the associations in monopartite network 
list_art


```
```
[['Decrease, AR activation', 'decrease, male anogenital distance'], ['Altered, Transcription of genes by AR', 'Antagonism, Androgen receptor'], ['Altered, Transcription of genes by AR', 'Decrease, DHT level'], ['Altered, Transcription of genes by AR', 'decrease, transcription of genes by AR'], ['Antagonism, Androgen receptor', 'Decrease, DHT level'], ['Antagonism, Androgen receptor', 'decrease, transcription of genes by AR'], ['Decrease, DHT level', 'decrease, transcription of genes by AR'], ['5alpha-reductase, inhibition', 'Decrease, AR activation']]
```

```{python}
dico_tar_red={}
co=0  
list_passe=[] 
for tar in tar_nm_py: 
  if(tar not in list_passe): 
    list_passe.append(tar) 
    for ar in list_art:
      if(ar[0]==tar or ar[1]==tar):
        co=co+1
    dico_tar_red[tar]=co
  co=0

```

```{python}
import math

list_h_aftr_ch_tar=[]
list_vrai_tar2=[]
ts_tar=r.ts_tar
for tar in ts_tar:
  if(tar in dico_tar_red.keys() and dico_tar_red[tar]!=0):
    list_vrai_tar2.append(tar)
  

```


## this part is to calculate the number of AOP event in each class
```{python}
nbr_sm={}
for event_class in r.event_type:
  nbr_sm[event_class]=0
  

i=0
for event_class in r.event_type:
  for tar in list_vrai_tar2:
    if(dic_tar_class[tar]==event_class):
      nbr_sm[dic_tar_class[tar]]=nbr_sm[dic_tar_class[tar]]+1
    i=i+1
  i=0

nbr_sm

nbr_sm_list=[]
for i in nbr_sm:
  nbr_sm_list.append(nbr_sm[i])

```
```
{'AdverseOutcome': 1, 'MolecularInitiatingEvent': 2, 'NewKeyEvent': 4}
```

## H after calculation

```{python}
tslp=clc_h[2]
ar=[]
passe=[]
liste_lp_gr=[]
lst_grph=[]
for lp in tslp:
  if(len(lp)!=1):
    for sm1 in lp:
      for sm2 in lp:
        ar=[sm1,sm2]
        if(sm1!= sm2 and [sm2,sm1] not in passe and ar not in passe):
          liste_lp_gr.append(sm1)
          liste_lp_gr.append(sm2)
    lst_grph.append(liste_lp_gr)
    liste_lp_gr=[]

```


## calculate Hafter for each vertex

```{python}

number_cliques=0
h_sm_lp_dic={}
for lp in tslp:
  if(len(lp)!=1):
    for sm in lp:
      h_sm_lp_dic[sm]=0

i=0
for lp in tslp:
  if(len(lp)!=1):
    for sm in lp:
      if h_sm_lp_dic[sm]< (-math.log(1/(2**(len(lp))))):
        h_sm_lp_dic[sm]=-math.log(1/(2**(len(lp))))  #H after for each vertex
        number_cliques=number_cliques+2**(len(lp)) #number of cliques for monopartite graph
    i=i+1


h_sm_lp=[]
for i in h_sm_lp_dic:
  h_sm_lp.append(h_sm_lp_dic[i]) 
```

```{python}
import pandas as pd
H_after_vertices = [h_sm_lp_dic]
H_after_vertices= pd.DataFrame(H_after_vertices,index=[0]).T
```

```{r}
H_after_vertices<-py$H_after_vertices
names(H_after_vertices)[1]<-"Hafter_vertices"
#write.table(H_after_vertices,"h_after.txt",row.names = T,sep="\t",quote=F)
```
```
[Antagonism, Androgen receptor: 2.77258872223978, Altered, Transcription of genes by AR: 2.77258872223978, Decrease, DHT level: 2.77258872223978, decrease, transcription of genes by AR: 2.77258872223978, 5alpha-reductase, inhibition:1.38629436111989,decrease, male anogenital distance: 1.38629436111989, Decrease, AR activation: 1.38629436111989]
```

```{python}
dic_h_aftr={}
for i in r.event_type:
  dic_h_aftr[i]=0
  
i=0
for event_class in r.event_type:
  for tar in list_vrai_tar2:
    if(dic_tar_class[tar]==event_class):
      dic_h_aftr[dic_tar_class[tar]]=dic_h_aftr[dic_tar_class[tar]]+h_sm_lp[i]
      nbr_sm[dic_tar_class[tar]]=nbr_sm[dic_tar_class[tar]]+1
    i=i+1
  i=0

```

# H after for global graph

```{python}

nbr_cliques=number_cliques

H_after=-nbr_cliques*(1/nbr_cliques)*math.log(1/nbr_cliques)
H_after

```
```
H_after= 4.330733340286331
```

```{python}
import math
list_lp_de_ar=[]
deb=0
for lp in values_list_lp2:
  if(len(lp)>=2):
    nbr_ar=int(math.factorial(len(lp))/(2*math.factorial(len(lp)-2)))
    fin=deb+nbr_ar
    list_lp_de_ar.append(list_art_avc_red[deb:fin])
    deb=fin
```


```{python}
import math
co=0
nbr_art=len(list_art)
list_art_h_bfr=[]
for art in list_art:
  for lp in list_lp_de_ar :
    if(art in lp or [art[1],art[0]] in lp ):
      co=co+1
  h_art=-(co/nbr_art)*math.log(co/nbr_art)
  co=0
  list_art_h_bfr.append(h_art)

```


```{python}

art_fml_h_bfr={}
for f in  r.event_type:
  art_fml_h_bfr[f]=0


i=0  
for fml in r.event_type:
  for ar in list_art:
    if(dic_tar_class[ar[0]]==fml or dic_tar_class[ar[1]]==fml ):
      art_fml_h_bfr[fml]=art_fml_h_bfr[fml]+list_art_h_bfr[i]
    i=i+1
  i=0

```


```{python}
h_art_aftr=[]
list_art_h_aftr=[]
for art in list_art:
  h_art_aftr=-(1/len(list_art))*math.log(1/len(list_art))
  list_art_h_aftr.append(h_art_aftr)

art_fml_h_aftr={}
for f in  r.event_type:
  art_fml_h_aftr[f]=0

```

# information of monopartite graph: 
-the number of edge in each AOP event class
-the number of vertex in each AOP event class
-the degree of vertices in each AOP event class
```{python}
nbr_ar={}
for event_class in r.event_type:
  nbr_ar[event_class]=0
  
i=0  
for fml in r.event_type:
  for ar in list_art:
    if(dic_tar_class[ar[0]]==fml or dic_tar_class[ar[1]]==fml ):
      art_fml_h_aftr[fml]=art_fml_h_aftr[fml]+list_art_h_aftr[i]
      nbr_ar[fml]=nbr_ar[fml]+1
    i=i+1
  i=0

nbr_art=[]
for i in nbr_ar:
  nbr_art.append(nbr_ar[i])  

```


```{python}
dic_deg_sm={}

for tar in list_vrai_tar2:
  dic_deg_sm[tar]=0

for tar in dic_deg_sm:
  for ar in list_art:
    if(tar == ar[0] or tar==ar[1]):
      dic_deg_sm[tar]=dic_deg_sm[tar]+1

```


```{python}
dic_deg_fml={}

for fml in r.event_type:
  dic_deg_fml[fml]=0

for event_class in r.event_type:
  for tar in list_vrai_tar2:
    if(dic_tar_class[tar]==event_class):
      dic_deg_fml[event_class]=dic_deg_fml[event_class]+dic_deg_sm[tar]
```


```{python}
fml_deg=[]
i=0
for fml in dic_deg_fml:
  if(nbr_sm_list[i]!=0):
    fml_deg.append(dic_deg_fml[fml]/nbr_sm_list[i]) 
    i=i+1
  else:
    fml_deg.append(0.0)
    i=i+1 


```

## monopartite network
```{r}
recap_gr_mono=data.frame(event_classs=names(diff_fmls[1:nbr_event_classs]),number_vertexs=py$nbr_sm_list,number_edges=py$nbr_art,degree_vertexs=py$fml_deg)
recap_gr_mono

write.table(recap_gr_mono, "information_graph_monopartite.csv", row.names=FALSE, sep="\t",dec=".", na=" ")
```

----------------------------------------loss of coverage calculation-----------------------------------------

# loss of coverage at edge level
```{python}

def calcul_cov(values_list_lp2,ok_each_edge): 
  dict_id_lp={}
  list_passee=[] 
  liste_lp=[]


  for lp in values_list_lp2:
    if(len(lp) != 1):
      liste_lp.append(lp)

  redo_lp_mono=redon_lp(liste_lp)[0]

  co=0
  for i in liste_lp:
    if( i not in list_passee):
      dict_id_lp[co]=i
      list_passee.append(i)
      co=co+1

  all_edges_possibles=[]
  lis_art=[]
  art=[] #edges
  dictio_list_art={}
  coo=0
  for lp in dict_id_lp.values():
    for efsec1 in lp:
      for efsec2 in lp:
        if(efsec1!=efsec2):
          art=[efsec1,efsec2]
          lis_art.append(art)
          if(art not in all_edges_possibles and [efsec2,efsec1] not in all_edges_possibles  ):
            all_edges_possibles.append(art)
    dictio_list_art[coo]=lis_art
    lis_art=[]
    coo=coo+1
  #loss of coverage at edge
  somme_frml=0
  nbr_lp=0
  coef_tot=0
  formule=0
  som_cov_art=0 #
  #calculate average of loss of coverage at edge level
  list_art_cov=[]
  for edge2 in all_edges_possibles:
    for iden in dictio_list_art:  
      if(edge2 in dictio_list_art[iden] ):
        nbr_lp=redo_lp_mono[iden]
        formule=nbr_lp*2/len(dict_id_lp[iden])
        somme_frml=somme_frml+formule
        coef_tot=coef_tot+nbr_lp
    if(coef_tot==0):
      cov=0
      coef_tot=1
    else:
      cov=1-(somme_frml/coef_tot)
    if(ok_each_edge==1):
      list_art_cov.append(cov)
    som_cov_art=som_cov_art+cov
    coef_tot=0
    somme_frml=0
  if(len(all_edges_possibles)==0):
    cov_moy=som_cov_art/1
  else:
    cov_moy=som_cov_art/len(all_edges_possibles)
  return (cov_moy,list_art_cov,all_edges_possibles)
  
```

# loss of coverage at edge level for global graph
```{python}
cov3_2=calcul_cov(values_list_lp2,1)
vect_cov_cy=cov3_2[1]
cov_gr=cov3_2[0]
cov_gr 

```
```
COV_edge global= 0.34375, 
COV_edge= [0.0, 0.5, 0.5, 0.25, 0.5, 0.5, 0.5, 0.0]
edge= [['Decrease, AR activation', 'decrease, male anogenital distance'], ['Altered, Transcription of genes by AR', 'Antagonism, Androgen receptor'], ['Altered, Transcription of genes by AR', 'Decrease, DHT level'], ['Altered, Transcription of genes by AR', 'decrease, transcription of genes by AR'], ['Antagonism, Androgen receptor', 'Decrease, DHT level'], ['Antagonism, Androgen receptor', 'decrease, transcription of genes by AR'], ['Decrease, DHT level', 'decrease, transcription of genes by AR'], ['5alpha-reductase, inhibition', 'Decrease, AR activation']]
```

```{python}
df_socs=r.diff_fmls[0:int(r.nbr_event_classs)]
dr_id_py=r.dr_id 

vect_nbr_drugs=[]
deb=0
co=0
fin2=0
drg_pass=[]
for t in range(int(r.nbr_event_classs)): 
  fin2=fin2+r.diff_fmls[t]
  for z in dr_id_py[deb:fin2]:
    if(z not in drg_pass):
      drg_pass.append(z)
      co=co+1
  vect_nbr_drugs.append(co) 
  deb=fin2
  co=0
  
```


```{python}
df_socs=r.diff_fmls[0:int(r.nbr_event_classs)]
deb=0
cov_e_classes=[]
list_art_class=[]
cov_art_class=[]
for i in range(len(df_socs)):
  fin=vect_nbr_drugs[i]+deb
  cov=calcul_cov(values_list_lp2[deb:fin],1)
  cov_e=cov[0]
  list_art_class.append(cov[2])
  cov_art_class.append(cov[1])
  deb=fin
  cov_e_classes.append(cov_e)

```

# loss of coverage at edge level
```{python}
H_vertexs1=[]
for tar in sm1:
  H_vertexs1.append(h_sm_lp_dic[tar])
H_vertexs2=[]
for tar in sm2:
  H_vertexs2.append(h_sm_lp_dic[tar])

class_sm2=[]
for tar in sm2:
  class_sm2.append(dic_tar_class[tar])
```

## extract AOP event associations in monopartite graph
```{python}
sm1=[]
sm2=[]
for ar in cov3_2[2]:
  if(len(ar)>1):
    sm1.append(ar[0])
    sm2.append(ar[1])
    
ls_class=[]
for sm in sm1:
  ls_class.append(dic_tar_class[sm])  

```

## extract loss of coverage at edge level
```{r}
vect_sm1=py$sm1
vect_sm2=py$sm2
vect_cov_cy=py$vect_cov_cy
vect_class=py$ls_class
class_sm2=py$class_sm2
loss_coverage_edge=data.frame(vertex1=vect_sm1,vertex2=vect_sm2,los_of_coverage_edge=vect_cov_cy,class_sm1=vect_class,class_sm2=class_sm2)
loss_coverage_edge

write.table(loss_coverage_edge,file="graph_monopartite_loss ofcoverage_edge.csv",quote = F,row.names = F,sep = "\t")

```
## loss of coverage for each vertex

```{python}
tts_edges=cov3_2[2]
cov_tts_edges=cov3_2[1]

list_tar=[] #la liste de tous les targets
for ar in tts_edges:
  if(ar[0] not in list_tar):
    list_tar.append(ar[0])
  if(ar[1] not in list_tar):
    list_tar.append(ar[1])


```


```{python}

dic_sm_cov={}

for key in list_tar:
  dic_sm_cov[key]=0

comb_art=0


for sm in list_tar:
  for i in range(len(tts_edges)) :
    if(sm in tts_edges[i]):
      dic_sm_cov[sm]=dic_sm_cov[sm]+cov_tts_edges[i]
      comb_art=comb_art+1
  dic_sm_cov[sm]=(dic_sm_cov[sm]/comb_art)
  comb_art=0

```

```{python}
vect_sm=[]
vect_cov=[]
for sm in dic_sm_cov:
  vect_sm.append(sm)
  vect_cov.append(dic_sm_cov[sm])
  
vect_class=[]
for sm in h_sm_lp_dic:
  vect_class.append(dic_tar_class[sm])

```

# result analysis

## extract result loss of coverage for each vertex
## plot figure: relationship increase in uncertainty-loss of coverage
```{r width=10 ,fig.height=15}
vect_sm=py$vect_sm
vect_cov=py$vect_cov
vect_class=py$vect_class

#loss of coverage for vertices
graph_cyto=data.frame(Target=vect_sm,loss_cov=vect_cov,class=vect_class)
graph_cyto



#plot figure: relationship increase in uncertainty-loss of coverage
#increase in uncertainty=Hafter-Hbefore
delta_h=vector(length = length(py$list_h_aftr_ch_tar) )#deltah: increase in uncertainty
for (i in 1:length(py$list_h_aftr_ch_tar)) {
  delta_h[i]=py$h_sm_lp[i]-py$list_h_bfr_ch_tar[i]
}

#pdf("Relaation_expo_Cov_H.pdf", height=20,width=20)
relationship={
plot(py$h_sm_lp~vect_cov,col=rainbow(nbr_event_classs),pch=19,font.axis=2, cex.main=2, cex.lab=2, cex.sub=3,xlab="Loss of coverage",ylab = "Increase in uncentainty [nats]" ,cex=2)
legend("topleft", legend=names(diff_fmls[1:nbr_event_classs]),col=rainbow(nbr_event_classs), pch=19,cex=3, title="event_classs", text.font=4, bg='lightblue')
}
relationship
```

## boxplot: increase in uncertainty and loss of coverage

```{r fig1, fig.height =5, fig.width = 20}

library(ggplot2)
#pdf("boxplot_perte_de_couverture.pdf", height=10,width=10)

p1=p=boxplot(graph_cyto$loss_cov~graph_cyto$class,col=rainbow(nbr_event_classs),xlab =("AOPevents"),cex.lab=1,cex.axis=1,ylab = ("Loss Of Coverage"),las=2)


#pdf("boxplot_augmentation_incertitude.pdf", height=10,width=30)
p2=boxplot(py$h_sm_lp~graph_cyto$class,col=rainbow(nbr_event_classs),xlab = "AOPevents",ylab="Increase In Uncertainty",cex.lab=1,cex.axis=1,las=2)

```














